---
title: Slide-Based Magic Move Demo
format: revealjs
revealjs-plugins:
  - magic-move
---

## Slope = 20 {.magic-move}

```{r}
#| label: "before"
#| dev: svg
library(ggplot2)
mtcars |>
  ggplot(aes(mpg, disp)) +
  geom_point(size = 5) +
  geom_abline(slope = 20, intercept = 0, linewidth = 5, color = "pink") +
  theme_minimal(base_size = 16)+
  lims(x = c(10, 35), y = c(100, 500))
```

## Slope = 10 {.magic-move}

```{r}
#| label: "after"
#| dev: svg
library(ggplot2)
mtcars |>
  ggplot(aes(mpg, disp)) +
  geom_abline(slope = 10, intercept = 0, linewidth = 5, color = "pink") +
  geom_point(size = 5) +
  theme_minimal(base_size = 16)+
  lims(x = c(10, 35), y = c(100, 500))
```

## Slope = 10 + jitter {.magic-move}

```{r}
#| label: "jitter"
#| dev: svg
library(ggplot2)
set.seed(1234)
mtcars |>
  ggplot(aes(mpg, disp)) +
  geom_abline(slope = 10, intercept = 0, linewidth = 5, color = "pink") +
  geom_jitter(width = 2, height = 5, size = 5) +
  theme_minimal(base_size = 16) +
  lims(x = c(10, 35), y = c(100, 500))
```


## Break



## Histogram - Normal {.magic-move}

```{r}
#| label: "hist-normal"
#| dev: svg
library(ggplot2)
set.seed(42)
data.frame(x = rnorm(1000, mean = 0, sd = 1)) |>
  ggplot(aes(x)) +
  geom_histogram(bins = 20, fill = "steelblue", color = "white") +
  theme_minimal(base_size = 16) +
  lims(x = c(-5, 5), y = c(0, 200))
```

## Histogram - Shifted {.magic-move}

```{r}
#| label: "hist-shifted"
#| dev: svg
library(ggplot2)
set.seed(42)
data.frame(x = rnorm(1000, mean = 2, sd = 1)) |>
  ggplot(aes(x)) +
  geom_histogram(bins = 20, fill = "steelblue", color = "white") +
  theme_minimal(base_size = 16) +
  lims(x = c(-5, 5), y = c(0, 200))
```

## Break

## Line Segments - Position 1 {.magic-move}

```{r}
#| label: "segments-1"
#| dev: svg
library(ggplot2)
data.frame(
  x = c(1, 2, 3, 4),
  xend = c(2, 3, 4, 5),
  y = c(1, 2, 1, 2),
  yend = c(2, 1, 2, 1)
) |>
  ggplot(aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_segment(linewidth = 3, color = "coral") +
  theme_minimal(base_size = 16) +
  lims(x = c(0, 6), y = c(0, 4))
```

## Line Segments - Position 2 {.magic-move}

```{r}
#| label: "segments-2"
#| dev: svg
library(ggplot2)
data.frame(
  x = c(1, 2, 3, 4),
  xend = c(2, 3, 4, 5),
  y = c(2, 1, 2, 1),
  yend = c(3, 2, 3, 2)
) |>
  ggplot(aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_segment(linewidth = 3, color = "coral") +
  theme_minimal(base_size = 16) +
  lims(x = c(0, 6), y = c(0, 4))
```

## Break

## Circles (grid) - Small {.magic-move}

```{r}
#| label: "circles-small"
#| dev: svg
library(grid)
grid.newpage()
grid.circle(
  x = c(0.2, 0.4, 0.6, 0.8),
  y = c(0.3, 0.5, 0.5, 0.3),
  r = 0.05,
  gp = gpar(fill = "steelblue", col = NA)
)
```

## Circles (grid) - Large {.magic-move}

```{r}
#| label: "circles-large"
#| dev: svg
library(grid)
grid.newpage()
grid.circle(
  x = c(0.2, 0.4, 0.6, 0.8),
  y = c(0.5, 0.7, 0.7, 0.5),
  r = 0.08,
  gp = gpar(fill = "steelblue", col = NA)
)
```

## Break

## Polyline (grid) - Wave 1 {.magic-move}

```{r}
#| label: "polyline-wave1"
#| dev: svg
library(grid)
grid.newpage()
grid.polyline(
  x = c(0.1, 0.3, 0.5, 0.7, 0.9),
  y = c(0.3, 0.7, 0.3, 0.7, 0.3),
  gp = gpar(col = "darkorange", lwd = 5)
)
```

## Polyline (grid) - Wave 2 {.magic-move}

```{r}
#| label: "polyline-wave2"
#| dev: svg
library(grid)
grid.newpage()
grid.polyline(
  x = c(0.1, 0.3, 0.5, 0.7, 0.9),
  y = c(0.5, 0.8, 0.5, 0.8, 0.5),
  gp = gpar(col = "darkorange", lwd = 5)
)
```

## Break

## Polygon (grid) - Triangle {.magic-move}

```{r}
#| label: "polygon-triangle"
#| dev: svg
library(grid)
grid.newpage()
grid.polygon(
  x = c(0.2, 0.5, 0.8),
  y = c(0.2, 0.8, 0.2),
  gp = gpar(fill = "purple", col = "white", lwd = 2)
)
```

## Polygon (grid) - Moved Triangle {.magic-move}

```{r}
#| label: "polygon-triangle-moved"
#| dev: svg
library(grid)
grid.newpage()
grid.polygon(
  x = c(0.3, 0.6, 0.9),
  y = c(0.3, 0.9, 0.3),
  gp = gpar(fill = "purple", col = "white", lwd = 2)
)
```

## Break

## Area Chart - Normal {.magic-move}

```{r}
#| label: "area-normal"
#| dev: svg
library(ggplot2)
data.frame(
  x = 1:10,
  y = c(1, 3, 2, 5, 4, 6, 5, 7, 6, 8)
) |>
  ggplot(aes(x, y)) +
  geom_area(fill = "forestgreen", alpha = 0.7) +
  theme_minimal(base_size = 16) +
  lims(x = c(0, 11), y = c(0, 10))
```

## Area Chart - Shifted {.magic-move}

```{r}
#| label: "area-shifted"
#| dev: svg
library(ggplot2)
data.frame(
  x = 1:10,
  y = c(2, 4, 3, 6, 5, 7, 6, 8, 7, 9)
) |>
  ggplot(aes(x, y)) +
  geom_area(fill = "forestgreen", alpha = 0.7) +
  theme_minimal(base_size = 16) +
  lims(x = c(0, 11), y = c(0, 10))
```

## Break

## Ellipse (polygon) - Wide {.magic-move}

```{r}
#| label: "ellipse-wide"
#| dev: svg
library(grid)
# Create ellipse as polygon
theta <- seq(0, 2*pi, length.out = 50)
ex <- 0.5 + 0.3 * cos(theta)
ey <- 0.5 + 0.15 * sin(theta)
grid.newpage()
grid.polygon(x = ex, y = ey, gp = gpar(fill = "tomato", col = "darkred", lwd = 3))
```

## Ellipse (polygon) - Tall {.magic-move}

```{r}
#| label: "ellipse-tall"
#| dev: svg
library(grid)
# Create ellipse as polygon
theta <- seq(0, 2*pi, length.out = 50)
ex <- 0.5 + 0.15 * cos(theta)
ey <- 0.5 + 0.3 * sin(theta)
grid.newpage()
grid.polygon(x = ex, y = ey, gp = gpar(fill = "tomato", col = "darkred", lwd = 3))
```

## Break

## Text (grid) - Position 1 {.magic-move}

```{r}
#| label: "text-pos1"
#| dev: svg
library(grid)
grid.newpage()
grid.text(
  label = c("Hello", "World", "ggplot2"),
  x = c(0.2, 0.5, 0.8),
  y = c(0.3, 0.5, 0.7),
  gp = gpar(fontsize = 24, col = "navy")
)
```

## Text (grid) - Position 2 {.magic-move}

```{r}
#| label: "text-pos2"
#| dev: svg
library(grid)
grid.newpage()
grid.text(
  label = c("Hello", "World", "ggplot2"),
  x = c(0.3, 0.6, 0.9),
  y = c(0.5, 0.7, 0.5),
  gp = gpar(fontsize = 24, col = "navy")
)
```

## Break

## Text Labels (ggplot2) - Before {.magic-move}

```{r}
#| label: "text-ggplot-before"
#| dev: svg
library(ggplot2)
data.frame(
  x = c(1, 2, 3),
  y = c(1, 3, 2),
  label = c("A", "B", "C")
) |>
  ggplot(aes(x, y, label = label)) +
  geom_point(size = 5, color = "steelblue") +
  geom_text(size = 8, vjust = -1) +
  theme_minimal(base_size = 16) +
  lims(x = c(0, 4), y = c(0, 5))
```

## Text Labels (ggplot2) - After {.magic-move}

```{r}
#| label: "text-ggplot-after"
#| dev: svg
library(ggplot2)
data.frame(
  x = c(1, 2, 3),
  y = c(2, 1, 3),
  label = c("A", "B", "C")
) |>
  ggplot(aes(x, y, label = label)) +
  geom_point(size = 5, color = "steelblue") +
  geom_text(size = 8, vjust = -1) +
  theme_minimal(base_size = 16) +
  lims(x = c(0, 4), y = c(0, 5))
```
