---
title: Slide-Based Magic Move Demo — Other R Plotting Packages
format: revealjs
revealjs-plugins:
  - magic-move
---

## Base R Histogram - Normal {.magic-move}

```{r}
#| label: "base-hist-normal"
#| dev: svg
set.seed(42)
hist(
  rnorm(1000, mean = 0, sd = 1),
  breaks = 20,
  col = "steelblue",
  border = "white",
  main = "",
  xlab = "x",
  xlim = c(-5, 5),
  ylim = c(0, 200)
)
```

## Base R Histogram - Shifted {.magic-move}

```{r}
#| label: "base-hist-shifted"
#| dev: svg
set.seed(42)
hist(
  rnorm(1000, mean = 2, sd = 1),
  breaks = 20,
  col = "steelblue",
  border = "white",
  main = "",
  xlab = "x",
  xlim = c(-5, 5),
  ylim = c(0, 200)
)
```

## Break

## Base R Scatter + Line - Slope 20 {.magic-move}

```{r}
#| label: "base-slope-20"
#| dev: svg
plot(
  mtcars$mpg, mtcars$disp,
  pch = 19, cex = 2,
  xlim = c(10, 35), ylim = c(100, 500),
  xlab = "mpg", ylab = "disp"
)
abline(a = 0, b = 20, col = "pink", lwd = 5)
```

## Base R Scatter + Line - Slope 10 {.magic-move}

```{r}
#| label: "base-slope-10"
#| dev: svg
plot(
  mtcars$mpg, mtcars$disp,
  pch = 19, cex = 2,
  xlim = c(10, 35), ylim = c(100, 500),
  xlab = "mpg", ylab = "disp"
)
abline(a = 0, b = 10, col = "pink", lwd = 5)
```

## Break

## Base R Barplot - Version 1 {.magic-move}

```{r}
#| label: "base-bar-v1"
#| dev: svg
barplot(
  c(A = 25, B = 40, C = 20, D = 15),
  col = "steelblue",
  border = NA,
  ylim = c(0, 50)
)
```

## Base R Barplot - Version 2 {.magic-move}

```{r}
#| label: "base-bar-v2"
#| dev: svg
barplot(
  c(A = 40, B = 15, C = 35, D = 25),
  col = "steelblue",
  border = NA,
  ylim = c(0, 50)
)
```

## Break

## Lattice Scatter - Position 1 {.magic-move}

```{r}
#| label: "lattice-xy-pos1"
#| dev: svg
library(lattice)
print(xyplot(
  disp ~ mpg, data = mtcars,
  pch = 19, cex = 1.5, col = "steelblue",
  xlim = c(10, 35), ylim = c(100, 500)
))
```

## Lattice Scatter - Position 2 {.magic-move}

```{r}
#| label: "lattice-xy-pos2"
#| dev: svg
library(lattice)
print(xyplot(
  disp ~ I(mpg + 5), data = mtcars,
  pch = 19, cex = 1.5, col = "steelblue",
  xlim = c(10, 35), ylim = c(100, 500),
  xlab = "mpg"
))
```

## Break

## Lattice Barchart - Version 1 {.magic-move}

```{r}
#| label: "lattice-bar-v1"
#| dev: svg
library(lattice)
print(barchart(
  c(A = 25, B = 40, C = 20, D = 15),
  col = "steelblue", horizontal = FALSE,
  ylim = c(0, 50)
))
```

## Lattice Barchart - Version 2 {.magic-move}

```{r}
#| label: "lattice-bar-v2"
#| dev: svg
library(lattice)
print(barchart(
  c(A = 40, B = 15, C = 35, D = 25),
  col = "steelblue", horizontal = FALSE,
  ylim = c(0, 50)
))
```

## Break

## ggiraph Points - Position 1 {.magic-move}

```{r}
#| label: "ggiraph-pos1"
library(ggplot2)
library(ggiraph)
p <- data.frame(x = c(1, 2, 3), y = c(1, 3, 2)) |>
  ggplot(aes(x, y)) +
  geom_point_interactive(size = 8, color = "steelblue") +
  theme_minimal(base_size = 16) +
  lims(x = c(0, 4), y = c(0, 4))
girafe(ggobj = p, width_svg = 6, height_svg = 4)
```

## ggiraph Points - Position 2 {.magic-move}

```{r}
#| label: "ggiraph-pos2"
library(ggplot2)
library(ggiraph)
p <- data.frame(x = c(1, 2, 3), y = c(2, 1, 3)) |>
  ggplot(aes(x, y)) +
  geom_point_interactive(size = 8, color = "steelblue") +
  theme_minimal(base_size = 16) +
  lims(x = c(0, 4), y = c(0, 4))
girafe(ggobj = p, width_svg = 6, height_svg = 4)
```
